---
title: "Week 4 Part 1 - CI t-tests"
author: "Lindsay Hafen"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 1. Confidence intervals
- If sample fits requirements in notes:
(always look at data, do exploratory data visualization, decide that the data fits)

- Create vector otter_length (put sample data into frame)
-t.test results are for a null of mean otter length = 0, so not super informative

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```

## T-test (1-sample t-test)
- See a claim: mean otter length is 50 inches
(look at data, do backgound exploration etc)
-test my sample against this claim

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```

## Two-sample t-test
- Welch does not assume equal variance, student t-test does


```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

- Probably not enough evidence to reject the null hypothesis...

## END PART 1

## Part 2: Two-sample t-test

- View data - using console and View function
- Basic wrangling (we want the compact car and SUV)

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))
```

## Exploratory data visualization

histograms: must understand distribution of data

```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins = 15) +
  facet_wrap(~class) #so far no concerns about distributions (seem close enough to normal distribution)
```

### Quantile-quantile plot to examine how close to normal distribution data is

```{r}
ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~class)
```

### Descriptive summary stats

n with empty () tells sample size

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarise(mean_cty = mean(cty), 
            sd_cty = sd(cty),
            n = n())

car_stats
```

### 2-sample t-test

Create vectors containing observations for each sample (city gas milage)

-If you use select, t-test will not work b/c it does not work with data frames, it works with vectors. Pull stores as a vector of values
```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

t.test(x = compact_sample, y = suv_sample)
```





