---
title: "Week 4 Part 1 - CI t-tests"
author: "Lindsay Hafen"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals
- If sample fits requirements in notes:
(always look at data, do exploratory data visualization, decide that the data fits)

- Create vector otter_length (put sample data into frame)
-t.test results are for a null of mean otter length = 0, so not super informative

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```

## T-test (1-sample t-test)
- See a claim: mean otter length is 50 inches
(look at data, do backgound exploration etc)
-test my sample against this claim

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```

## Two-sample t-test
- Welch does not assume equal variance, student t-test does


```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

- Probably not enough evidence to reject the null hypothesis...


